### 2019-03-04 report/final-report.tex
opticianq
Checkpoint

\subsection{Simple Symmetric Synthesis Algorithms}
We implemented simple symmetric lenses as an extension to
Boomerang~\cite{boomerang}.  
We also integrated our synthesis engine into Boomerang, allowing users
to write synthesis tasks 
alongside lens combinators, incorporate synthesis results into manually-written
lenses, and reference previously defined lenses during synthesis. All experiments
were performed on a 2.5 GHz Intel Core i7 processor with 16 GB of 1600 MHz DDR3
running macOS Mojave.

\paragraph*{Benchmark Suite Construction}
Our benchmarks are drawn from three different sources.
\begin{enumerate}
\item We adapted 8 data cleaning benchmarks from Flash Fill~\cite{flashfill}. Flash Fill data
  cleaning tasks are either derived from online help forums or taken from the
  Excel product team. Note that our tool produces bidirectional transformations
  rather than one-way transformers like Flash Fill. We ensure one direction of
  our bidirectional transformers performs the same unidirectional transformation
  as Flash Fill---the other direction is determined from the round-tripping
  laws. None of these benchmarks were bijective.
\item We adapted 29 benchmarks from Augeas~\cite{augeas}. Augeas is a utility
  that bidirectionally converts between Linux configuration files and an
  in-memory dictionaries. In our benchmarks, we synthesize lenses between Linux
  configuration files and serialized versions of Augeas dictionaries. Because
  these benchmarks merely transformed the information into a structured form,
  synthesized lenses were all bijective.
\item We created 11 additional benchmarks 
  derived from real-world examples and/or the bidirectional programming
  literature. These tasks range from synchronizing REST and JSON web resource
  descriptions to synchronizing BibTeX and EndNote citation descriptions. Five
  of these benchmarks were not bijective lenses.
\end{enumerate}

@@

To determine whether the system can synthesize desired lenses, we ran
it interactively on all 48 benchmark tasks, working with the system to
create sufficient examples and provide useful relevance annotations
(\IE, \emph{essential} and \emph{irrelevant} markings, written as
\SRequire and \Skip, respectively).
In all cases, the desired lens was obtained.
%
The majority of the tasks required only a single example and none required
more than three examples to synthesize the desired lens.
%
Providing relevance annotations 
was needed in only 8 of the 48 tasks. In
practice, we found that adding such annotations was quite easy: if manual inspection
of the lens showed there were too few \IdentityLens{}s, and too many
\Disconnect{}s\footnote{
A \Disconnect{} is a lens combinator that marks a place where
information appears in one format but not the 
other: there is a \emph{disconnect} between the two formats. 
}
  or merges, we would add \SRequire annotations. If synthesis took
too long, we would add \Skip annotations.
%
We verified that the default running mode of our synthesis tool
(\SSOpt{}) generated the 
correct lenses the way programmers often validate their programs: we
manually inspected the code and ran unit tests on the synthesized
code. To determine whether the synthesis procedure generated the
correct lens when running in modes other than \SSOpt{}, we compared
generated lens to the lens synthesized by \SSOpt{}.

@@

For each benchmark in the suite and each mode, we ran the system with a timeout
of 60 seconds, averaging the result over 5 runs. Figure~\ref{fig:times}
summarizes the results of these tests. We find that our algorithm is able to
synthesize all of the benchmarks in under 30 seconds. Without compositional
synthesis, the synthesis algorithm is able to solve 26 out of 48 problem instances.

@@

To compare to the existing bijective synthesis algorithm, we run our symmetric
synthesis algorithm on the original Optician benchmarks, comprised of
39 bijective synthesis tasks.\footnote{We had to slightly alter four of these
benchmarks, either by providing additional examples or by adding \SRequire annotations.
Without these alterations, symmetric synthesis yielded a lens that fit
the specification but that was undesired.}
To perform this comparison, we synthesized lenses in two modes:
\vskip 2ex
\begin{tabulary}{\linewidth}{rL}
  \BSOpt{}: & The existing bijective synthesis
              algorithm with all optimizations enabled.\\
  \SSOpt{}: & The symmetric synthesis algorithm with all optimizations enabled.\\
\end{tabulary}\\[2ex]
\noindent
For each benchmark, we ran it in both modes with a
timeout of 60 seconds and averaged the result over 5 runs.
Figure~\ref{fig:times_bijective} summarizes the results of these tests. On
average, \SSOpt{} took 1.3 times (0.5 seconds) longer to complete than
\BSOpt{}. The slowest completed benchmark for both synthesis algorithms is
\texttt{xml\_to\_augeas.boom}, a benchmark that converts arbitrary XML up to
depth 3 into a serialized version of the structured dictionary representation
used in Augeas. This benchmark takes 18.9 seconds for the symmetric synthesis
algorithm to complete, and 9.3 seconds the bijective synthesis algorithm to
complete.

@@

Figure~\ref{fig:metric} summarizes the result of these experiments. The data
reveal that the information-theoretic metric is critical for finding the correct
lens: Only 10 of the benchmarks succeeded when running in \CCOpt{} mode. The
termination condition is also quite important. When running in \FLOpt{} mode,
the algorithm only discovers 5 lenses, which shows that the first class that
contains a satisfying lens is rarely the correct class. However, our algorithm
is not perfect and fails when either it is very difficult to find the desired
lens (necessitating \SRequire) or when a large amount of data is projected
(necessitating \Skip). Without any annotations, our algorithm finds the correct
lens for 40 of our 48 benchmarks; eight required relevance annotations to find
the correct lens.
% end evaluation

>>>>

\subsection{Simple Symmetric Lens Synthesis}
Finally, we implemented simple symmetric lenses as an extension to
Boomerang~\cite{boomerang}.  
This allows users
to write synthesis tasks 
alongside lens combinators, incorporate synthesis results into manually-written
lenses, and reference previously defined lenses during synthesis. All experiments
were performed on a 2.5 GHz Intel Core i7 processor with 16 GB of 1600 MHz DDR3
running macOS Mojave.

\paragraph*{Benchmark Suite Construction}
Our benchmarks for this experiment are drawn from three different sources.
\begin{enumerate}
\item We adapted 8 data cleaning benchmarks from Flash Fill~\cite{flashfill}. Flash Fill data
  cleaning tasks are either derived from online help forums or taken from the
  Excel product team. Note that our tool produces bidirectional transformations
  rather than one-way transformers like Flash Fill. We ensure one direction of
  our bidirectional transformers performs the same unidirectional transformation
  as Flash Fill---the other direction is determined from the round-tripping
  laws. None of these benchmarks were bijective.
\item We adapted 29 benchmarks from Augeas~\cite{augeas}. Because
  these benchmarks merely transform the information into a structured form,
  synthesized lenses were all bijective.
\item We created 11 additional benchmarks 
  derived from real-world examples and/or the bidirectional programming
  literature. These tasks range from synchronizing REST and JSON web resource
  descriptions to synchronizing BibTeX and EndNote citation descriptions. Five
  of these benchmarks were not bijective lenses.
\end{enumerate}

@@

To determine whether the system can synthesize desired lenses, we ran
it interactively on all 48 benchmark tasks, working with the system to
create sufficient examples and provide useful relevance annotations
(\IE, \emph{essential} and \emph{irrelevant} markings, written as
\SRequire and \Skip, respectively).
In all cases, the desired lens was obtained.
%
The majority of the tasks required only a single example and none required
more than three examples to synthesize the desired lens.
%
Providing relevance annotations 
was needed in only 8 of the 48 tasks. In
practice, we found that adding such annotations was quite easy: if manual inspection
of the lens showed there were too few \IdentityLens{}s, and too many
\Disconnect{}s\footnote{
Recall that \Disconnect{} is a lens combinator that marks a place where
information appears in one format but not the 
other: there is a \emph{disconnect} between the two formats. 
}
  or merges, we would add \SRequire annotations. If synthesis took
too long, we would add \Skip annotations.
%
We verified that the default running mode of our synthesis tool
(\SSOpt{}) generated the 
correct lenses the way programmers often validate their programs: we
manually inspected the code and ran unit tests on the synthesized
code. To determine whether the synthesis procedure generated the
correct lens when running in modes other than \SSOpt{}, we compared
generated lens to the lens synthesized by \SSOpt{}.

@@

For each benchmark in the suite and each mode, we ran the system with a timeout
of 60 seconds, averaging the result over 5 runs. Figure~\ref{fig:times}
summarizes the results of these tests. We found that our algorithm is able to
synthesize all of the benchmarks in under 30 seconds. Without compositional
synthesis, the synthesis algorithm is able to solve 26 out of 48 problem instances.

@@

To compare to the existing bijective synthesis algorithm, we ran our symmetric
synthesis algorithm on the original Optician benchmarks, comprised of
39 bijective synthesis tasks.\footnote{We had to slightly alter four of these
benchmarks, either by providing additional examples or by adding \SRequire annotations.
Without these alterations, symmetric synthesis yielded a lens that fit
the specification but that was not what the programmer wanted.}
To perform this comparison, we synthesized lenses in two modes:
\vskip 2ex
\begin{tabulary}{\linewidth}{rL}
  \BSOpt{}: & The existing bijective synthesis
              algorithm with all optimizations enabled.\\
  \SSOpt{}: & The symmetric synthesis algorithm with all optimizations enabled.\\
\end{tabulary}\\[2ex]
\noindent
For each benchmark, we ran it in both modes with a
timeout of 60 seconds and averaged the result over 5 runs.
Figure~\ref{fig:times_bijective} summarizes the results of these tests. On
average, \SSOpt{} took 1.3 times (0.5 seconds) longer to complete than
\BSOpt{}. The slowest completed benchmark for both synthesis algorithms is
\texttt{xml\_to\_augeas.boom}, a benchmark that converts arbitrary XML up to
depth 3 into a serialized version of the structured dictionary representation
used in Augeas. This benchmark takes 18.9 seconds for the symmetric synthesis
algorithm to complete, and 9.3 seconds the bijective synthesis algorithm to
complete.

@@

Figure~\ref{fig:metric} summarizes the result of these experiments. The data
reveal that the information-theoretic metric is critical for finding the correct
lens: Only 10 of the benchmarks succeeded when running in \CCOpt{} mode. The
termination condition is also quite important. When running in \FLOpt{} mode,
the algorithm only discovers 5 lenses, which shows that the first class that
contains a satisfying lens is rarely the correct class. However, our algorithm
is not perfect and fails when either it is very difficult to find the desired
lens (necessitating \SRequire) or when a large amount of data is projected
(necessitating \Skip). Without any annotations, our algorithm finds the correct
lens for 40 of our 48 benchmarks; the other eight required relevance
annotations to find the correct lens.
% end evaluation
